\PaperTitle

### 2024-05-02 Final_Report/paper.tex
added data colection

\subsection{Data Preparation and Processing}

\subsubsection{Feature Selection}
\subsubsection{Data Formatting}

>>>>

\subsection{Data Preparation and Processing}
To maintain normalized representation in all the collected datasets, a process of data harmonization 
was applied after collecting the necessary data. The dataset with the minimum number of observations is identified and accounted for when
truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
This process ensures a balanced yet unbaised dataset that maximizes the effectivness of our models.

\subsubsection{Feature Selection}

\subsubsection{Data Formatting}
